%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{Acknowledgements}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
Finally.
I have been waiting sooooo long to write in the first person.
These acknowledgements would sound \textit{pretty} hollow coming from "the author".
I might even use a couple contractions\ldots

I would like to begin by thanking my advisor, Simon Trebst.
Obviously, you gave me the opportunity to do this work in the first place, but you've also always given me the support to complete it.
Without your leadership this thesis would never have come to fruition.

Next I would like to thank Achim Rosch and Markus Gr\"uninger for taking the time to evaluate my work and for agreeing to act as secondary advisor and chairman of my thesis committee, respectively.

I owe a huuuuuuge "thank-you" to Petra Neubauer-Guenther for the countless times she has been of indispensable help to me, guided me through the often Vogonic levels of bureaucracy and served as a friend and confidante during both the good and the trying times.

Thank you to Peter Br\"ocker, Max Gerlach and Johannes Helmes for the office atmosphere I enjoyed for the bulk of my time here until you all went and graduated on me.
\textit{Special} thanks goes to Peter, Tim, Finn and Henry for the fruitful discussions we somewhat occasionally had.
Even more specialer thanks goes to Tim, Finn and Henry for proofreading parts of this thesis.

I would like to extend a very \textit{extra} special "thank-you" to my girlfriend, Bahar.
Thank you for loving and supporting me and for keeping me grounded during these final stages of my studies.
Thank you for proofreading \textit{huge} chunks of my thesis and for discussing physics with me when you likely didn't want to, but also for not letting me forget that there is a life outside of my thesis.
Thank you for the khoresh bademjan :P

And finally, thank you to my family.
You all have always supported me in everything I do (for better or for worse\ldots) and I can't begin to express how much it means to me.
So I won't.
Just use your imagination\ldots (It's ok, they're my \textit{family}. They know me.)